Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-21 paper.tex
Revising English
Changing sentences which sound awkward and merging them so that text flows more easily

Refs #11

The problem to solve in this work is the forecasting of sales for new launched books in the Spanish market, considering a set of `pre-sales variables'.
The objective is to offer a tool for publishers which will aid them to decide the best print run for a new book before its publication process starts. This is a forecasting problem for which no specific historical data are available, since the same book has not been previously published.
However, we have considered data about other previously published books and have taken as reference a set of variables (or features), related with the book publication process.

The training dataset includes historical data about 6083 books published in Spain for several years, with an initial set of 50 variables per pattern. It has been provided by the Spanish publishing company Trevenque Editorial S.L.. Table
\ref{tabla:paramsOrig50} shows the initial set of variables describing
each book.

>>>>

The problem to solve in this work is the forecasting of sales for new
launched books in the Spanish market, considering a set of `pre-sales
variables' or at least variables that are under the control of the
publisher before the book is going to be released to bookstores. The
objective is to offer a tool for publishers which will help them to
decide the best print run for a new book before its publication
process starts. This is a forecasting problem for which no specific
historical data are available and thus it is not simply a matter of
analyzing a time series, instead, we have considered data about other,
previously published, books and have taken as reference a set of
variables (or features), 
related with the book publication process.

The training dataset includes historical data about 6083 books
published in Spain for several years, with an initial set of 50
variables per pattern. It has been provided by the Spanish publishing
company Trevenque Editorial S.L. Table 
\ref{tabla:paramsOrig50} shows the initial set of variables describing
each book.
